---
title: "Equaker"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Equaker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = TRUE,
  warning = TRUE,
  fig.width = 7,
  fig.height = 3,
  fig.align = "center",
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Equaker)
```
`Equaker` allows users to load in a data file from NOAA regarding eartquake data and generate a map.

## eq_readIn_data 
reads in the tab delimited data file and returns a data frame

## eq_clean_data
Cleans the raw data to remove colons from Location Name for use later.
```{r cleanDataFile, eval = TRUE}
library(dplyr)
library(magrittr)
library(stringr)
library(lubridate)
library(readr)
df = readr::read_delim("./results.tsv", delim = "\t") %>% eq_clean_data()
```

## eq_location_clean
    Cleans the original location_name to remove the unwanted formatting which includes a semi-colon. 
    Read in the raw data file then run the eq_clean_data function followed by eq_location_clean to 
    format the LOCATION_NAME to something more readable for use when plotting.
```{r cleanLocationName, eval = TRUE}
library(readr)
library(stringr)
library(dplyr)
library(magrittr)
library(lubridate)
df = readr::read_delim("./results.tsv", delim = "\t") %>% eq_clean_data() %>%
eq_location_clean()
```

## geom_timeline
filters the data to show events that occured in the USA past a certain date.
```{r timeline, eval = TRUE}
library(lubridate)
library(dplyr)
library(ggplot2)
library(magrittr)
library(readr)
df = readr::read_delim("./results.tsv", delim = "\t") %>% eq_clean_data() %>% eq_location_clean()
geom_timeline(df)
```

## geom_timeline_label
adds another layer to the map with text
```{r timelineLabel, eval = TRUE}
library(lubridate)
library(dplyr)
library(ggplot2)
library(magrittr)
library(readr)
df = readr::read_delim("./results.tsv", delim = "\t") %>% eq_clean_data() %>% eq_location_clean()
geom_timeline_label(df)
```

## eq_create_label
this will get details to list on popup annotations for eq_map 
```{r labeld, eval = TRUE}
library(lubridate)
library(dplyr)
library(purrr)
library(magrittr)
library(ggplot2)
eq_create_label(df)
```

## eq_map
this will generate a global map with events show on interactive map
```{r mapping, eval = FALSE}
library(readr)
library(lubridate)
library(dplyr)
library(leaflet)
library(magrittr)
library(ggplot2)
library(leaflet)
library(purrr)
df = readr::read_delim("./results.tsv", delim = "\t") %>% eq_clean_data() %>% eq_location_clean()
geom_timeline_label(df)
eq_map(df)
```


