---
title: "Equaker"
author: "Juthy"
date: "5/19/2019"
output:
  html_document:
    df_print: paged
vignette: |
  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`Equaker` allows users to load in a data file from NOAA regarding eartquake data and generate a map.

## eq_readIn_data 
reads in the tab delimited data file and returns a data frame

```{r readDataFile}
library(readr)
df <- eq_readIn_data("./data/results.tsv")
```

## eq_clean_data
Cleans the raw data to remove colons from Location Name for use later.
```{r cleanDataFile}
library(dplyr)
library(purrr)
library(magrittr)
library(stringr)
df_clean <- eq_clean_data(df)
```

## geom_timeline
filters the data to show events that occured in the USA past a certain date.
```{r timeline}
library(dplyr)
library(ggplot)
library(magrittr)
geom_timeline(df_clean)
```

## geom_timeline_label
adds another layer to the map with text
```{r timelineLabel}
library(dplyr)
library(ggplot)
library(magrittr)
geom_timeline_label(df_clean)
```

## eq_map
this will generate a global map with events show on interactive map
```{r mapping}
library(dplyr)
library(leaflet)
library(magrittr)
eq_map(df_filtered)
{\tt plot(eq_map(df_filtered))}
```

## eq_create_label
this will get details to list on popup annotations for eq_map 
```{r labeld}
library(dplyr)
library(purrr)
library(magrittr)
eq_create_label(df_filtered)
```
